---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)

```

# conquer2

<!-- badges: start -->
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Package Version](https://img.shields.io/badge/version-0.0.1-blue.svg)](https://cran.r-project.org/package=yourPackageName)
<!-- badges: end -->

conquer2 is merely an edited fork of the package `conquer`. The package `conquer` is a wonderfully fast package for solving quantile regression models that enforces the existence of an intercept. This fork of the package merely removes the intercept and solves no-intercept models. For any references or information regarding how the package works we refer you to the original [repository](https://github.com/XiaoouPan/conquer) and [manual](https://cran.r-project.org/web/packages/conquer/conquer.pdf)

## Installation

You can install the development version of conquer2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alvaromc317/conquer2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(conquer2)

set.seed(123)

n = 500
p = 10
p2 = 5

X = matrix(rnorm(n * p, mean=2), ncol = p)
beta = c(rep(0, (p-p2)), 1:p2)
eps = rnorm(n, sd = 0.3)
y = X %*% beta + eps

model = conquer(X, y, tau=0.5)

```

```{r, include=F}

library(quantreg)
quantreg_model = quantreg::rq(y~-1+X, tau=0.5)

df = tibble(`True coef` = beta,
            `Conquer coef` = model$coeff,
            `Quantreg coef` = quantreg_model$coefficients)

df = round(df, 2)
```

```{r, echo=F}
df
```
