---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)

```

# conquer2

<!-- badges: start -->
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Package Version](https://img.shields.io/badge/version-0.0.1-blue.svg)](https://cran.r-project.org/package=yourPackageName)
<!-- badges: end -->

conquer2 is an edited fork of the package `conquer`. The package `conquer` is a wonderfully fast package for solving quantile regression models that enforces the existence of an intercept. This fork of the package merely removes the intercept and solves no-intercept models. For any references or information regarding how the package works we refer you to the original [repository](https://github.com/XiaoouPan/conquer) and [manual](https://cran.r-project.org/web/packages/conquer/conquer.pdf)

## Installation

You can install the development version of conquer2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alvaromc317/conquer2")
```

## Example 1: unpenalized comparison

This is a basic example which shows you how to solve a common problem:

```{r}
set.seed(123)

n = 500
p = 10
p2 = 5

X = matrix(rnorm(n * p, mean=2), ncol = p)
beta = c(rep(0, (p-p2)), 1:p2)
eps = rnorm(n, sd = 0.3)
y = X %*% beta + eps
```

```{r}
library(conquer2)
model = conquer(X, y, tau=0.5)
```

```{r}
library(quantreg)
quantreg_model = quantreg::rq(y~-1+X, tau=0.5)
```

```{r, include=F}
df = tibble(`True coef` = beta,
            `Conquer coef` = model$coeff,
            `Quantreg coef` = quantreg_model$coefficients)

df = round(df, 2)
```

```{r, echo=F}
df %>% kableExtra::kable()
```

## Example 2: Penalized quantile regression

The following script solves a range of penalized quantile regression models with a lasso penalty

```{r}
lambda_values <- 10^seq(-0.1, 0.1, length.out=100)
coefficients_matrix <- matrix(0, nrow = length(lambda_values), ncol = ncol(X))

for (i in seq_along(lambda_values))
{
  model <- conquer2::conquer.reg(X, y, penalty = 'lasso', lambda = lambda_values[i], tau = 0.5)
  coefficients_matrix[i, ] <- model$coeff
}

# Plot the coefficient paths
# Use matplot to plot multiple lines (one for each coefficient)
matplot(
  log(lambda_values, base=10),           # Lambda values on log scale
  coefficients_matrix,          # Coefficient matrix
  type = 'l',                   # Line plot
  lty = 1,                      # Line type
  lwd = 2,                      # Line width
  col = rainbow(ncol(X)),       # Different color for each line
  xlab = 'log(lambda)',         # X-axis label
  ylab = 'Coefficient Values',  # Y-axis label
  main = 'LASSO Coefficient Paths'  # Plot title
)
```

## Example 3: Group lasso penalty

```{r}
model <- conquer2::conquer.reg(X, y, penalty = 'group', group=1:10, lambda = 0.01, tau = 0.5)
model$coeff
```
